\chapter{Active knowledge extraction from cyclic voltammetry}\label{chapter3}
Cyclic Voltammetry~(CV) is an electro-chemical characterization technique used in an initial material screening for desired properties and to extract information about electro-chemical reactions.
In some applications, to extract kinetic information of the associated reactions (e.g., rate constants and turn over frequencies), CV curve should have a specific shape (for example an S-shape). 
However, often the settings to obtain such curve are not known \textit{a priori}. 
In this chapter, an active search framework is defined to accelerate identification of settings that enable knowledge extraction from CV experiments.
Towards this goal, a function space representation of CV responses is used in combination with Bayesian Model Selection (BMS) method to efficiently label the response to be either \textit{S-shape} or not \textit{S-shape}. 
Using an active search with BMS oracle, we report a linear target identification in a 6-dimensional design space (comprising of thermodynamic, mass transfer and solution variables as dimensions). 
The framework has the potential to be a powerful virtual screening technique for molecular catalysts, bi-functional fuel cell catalysts etc.


\section{Introduction}
\input{Chapter-3/introduction.tex}
\input{Chapter-3/method_al}
\input{Chapter-3/method_bms}
\input{Chapter-3/method_gps}

\section{Results}
To demonstrate the application of active search for S-shaped CV curves, we choose a classic EC-mechanism, that consists of two reactions: E and C (\Cref{E} and \Cref{C}) corresponding to one electron transfer reaction (E) and one chemical reaction (C), respectively. 
EC-mechanism is selected as it is a well studied mechanism~\cite{rountree2014evaluation, costentin2015cyclic} that produces a variety of CV shapes thus serves as a good test case for the oracle proposed in this paper. 
In this work, we use the MECSim simulator~\cite{MECSim} to generate CV curves on demand. 

\input{Chapter-3/results_data}
\input{Chapter-3/results_abs}

\section{Conclusion and future work}
In conclusion, we defined and evaluated a \(\mathcal{GP}\)-based oracle for materials discovery using cyclic voltammetry.
Next, we combined the oracle with a state-of-the-art active batch search to identify condition resulting in the targeted shape of CV curve. 
We demonstrated a robust high throughput combinatorial search to find the target responses using only \(<6\%\) of total number of CV experiments from the corresponding exhaustive search (with a discrete sampling of modest 5 levels per dimension). 

This work has implications in identification of characterization conditions where kinetic knowledge extraction from the cyclic voltammetry can be preformed more effectively. 
Specifically, we have illustrated a framework that can be used to identify S-shaped CV curves. 
Once S-shaped CV curve is obtained, a foot of the wave analysis can be applied ~\cite{FOWA} to extract rate constant for rate determining step, overpotential dependent turn over frequency etc.
In this sense our method has applications in accelerated knowledge extraction, with the application in screening for target catalysts including the bi-functional alkaline fuel cell catalysts that motivated this work.

\input{Chapter-3/Supplementary.tex}
