% Place abstract below.
Materials design and discovery through the high-throughput exploration of materials space has been recognized as a new paradigm in materials science. However, typical high-throughput exploration methods deliver high-dimensional and very diverse data sets that pose the challenge of extracting the key features and patterns that could guide the discovery process. Unraveling patterns is a non-trivial task as quite often the underlying physical phenomena are uncertain and latent variables governing the performance are mainly unknown. 

In this thesis, I develop data-driven approaches to accelerate understanding of materials properties from high throughput data exploration pipeline.
The approaches involve building physics-informed representations for multi-variate correlative study of diverse set of data sets including cyclic voltammetry, XRD signals and phase diagrams. 
We use examples from different studies to showcase the usage of data representation for the several types of tasks from the exploratory data analysis that include an active knowledge extraction and down selection from high-throughput datasets. 
For example, we demonstrate an active learning approach to accelerate a high-throughput knowledge extraction by an order of magnitude. 
The approaches and the analysis included in this thesis highlight the importance of identifying suitable representations of data for down stream analysis both qualitatively (good set of clusters in clustering) and empirically (accelerated target search in active searching). 


